A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Refer back to JS example to reinforce the advantage of typing.

\begin{listingfloat}
\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

Now that we have seen how to implement both network communication, we are ready
to revisit the chatbox program, this time using our improved programming model.
Since we are now writing the entire application, both client and server, as
opposed to the client part from our motivating example, our program has three
new responsibilities.

@@

Having implemented our three server operations, all that's left is to tie them
to the client. We start by creating an \lstinline!MVar! to hold the server
state and exporting our three server operations.

@@

%\acks
%
%Acknowledgments, if needed.

>>>>

\label{sec:jsexample}
\begin{listingfloat}
\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

Now that we have seen how to implement both network communication, we are ready
to revisit the chatbox program from section \ref{sec:jsexample}, this time
using our improved programming model. Since we are now writing the entire
application, both client and server, as opposed to the client part from our
motivating example, our program has three new responsibilities.

@@

Having implemented our three server operations, all that's left is to tie them
to the client. In this tying, we see our main advantage over the Javascript
version in section \ref{sec:jsexample} in action: the \lstinline!export!
function builds a strongly typed bridge between the client and the server,
ensuring that any future enhancements to our chatbox program are made safely,
in one place, instead of being spread about throughout two disjoint code bases.

@@
